Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-13 paper.qmd
added confusion matrix with 6 classes and new detour

UMAP_pbmc_with_true_label |>
    ggplot(aes(x = UMAP1,
               y = UMAP2, color = true_class_label))+
    geom_point(alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3", "#a6d854", "#ffd92f", "black")) +
  # geom_text(aes(x=UMAP1,y = UMAP2,label = cell_label), data = class_avg,inherit.aes = F, color = "black",fontface = "bold",size = 2) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

>>>>

UMAP_pbmc_with_true_label |>
    ggplot(aes(x = UMAP1,
               y = UMAP2, color = true_class_label))+
    geom_point(alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#d82cd3", "#49df20", "#619cff", "#000000", "#df2020", "#ffbd61", "yellow")) +
  # geom_text(aes(x=UMAP1,y = UMAP2,label = cell_label), data = class_avg,inherit.aes = F, color = "black",fontface = "bold",size = 2) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

## Import detour results
detour_results8 <- read_csv("data/pbmc/pbmc_3k_festem/detourr_export8.csv")
detour_results8 <- detour_results8 |>
  dplyr::mutate(ID = training_data_pbmc$ID)

table(UMAP_pbmc_with_true_label$true_class_label, detour_results8$colour)
